\documentclass{article}
\setlength{\parskip}{1em}
\linespread{1.25}
\begin{document}
\begin{center}
{\Huge An App for Fan Based Live Sports Audio Commentary\\[5cm]}

{\Large Sam Mai

BSc Computer Science

Submission Date: \today

Supervisor: Harry Strange}
\end{center}
\newpage
\begin{center}
{\Large \textbf{Abstract}}
\end{center}
The project involves development of an Android application to provide football fans a social platform to interact with others and motivates users to get involved through live streaming capabilities. The application will be supported by two different servers, one is used for live streaming capabilities and another back-end server to store users' information. The aim of the project is to provide a simple social platorm for Football fans where they can more involved with the sport. The main goal of the project is to develop an Android application that can perform a range of functionalities including: live streaming, live chat and socialising with other users. The main challenge of the project is to ensure the quality of live streams and the experience these live streams will bring to other users.\par
\noindent The project is carried out in an iterative manner, goals and objectives are broken down into smaller objectives that can be achieved in a shorter period of time which in turn would be broken down into a list of weekly objectives. The project involved understandings of different technologies: Android development, PHP scripting + MySQL, Firebase Cloud Messaging and Wowza GoCoder SDK.\par
\noindent The project resulted in a fully functional and tested Android application that achieved the set aims and goals along with a functional back-end server. A document has been produced that provides all technical details about the whole system including a user manual to demonstrate the application's capabilities and a system manual to assist further development.\\
\end{document}